Combining of local and global search in the parallel nested optimization scheme\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-02-13 2020/PAVT_Nested_Full/pavt_paper.tex
emails of all authors

\begin{document}
\mainmatter              % start of a contribution
%
\title{Combining of local and global search in the parallel nested optimization scheme 
\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
%
\titlerunning{Combining of local and global search}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Konstantin Barkalov\letter\orcidID{0000-0001-5273-2471} \and Ilya 
Lebedev\orcidID{0000-0002-8736-0652} \and Maria Kocheganova \orcidID{0000-0002-4722-6299} 
\and Victor Gergel \orcidID{0000-0002-4013-2329}}
%
\authorrunning{Konstantin Barkalov et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Konstantin Barkalov and Ilya Lebedev, and Maria Kocheganova}
%
\institute{Lobachevsky State University of Nizhni Novgorod, Russia  \\
	\email{konstantin.barkalov@itmm.unn.ru}
}

>>>>

\begin{document}
\mainmatter              % start of a contribution
%
\title{Combining of local and global search in the parallel nested optimization scheme\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}
}
%
\titlerunning{Combining of local and global search}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Konstantin Barkalov\letter\orcidID{0000-0001-5273-2471} \and Ilya 
Lebedev\orcidID{0000-0002-8736-0652} \and Maria Kocheganova \orcidID{0000-0002-4722-6299} 
\and Victor Gergel \orcidID{0000-0002-4013-2329}}
%
\authorrunning{Konstantin Barkalov et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Konstantin Barkalov and Ilya Lebedev and Maria Kocheganova and Victor Gergel}
%
\institute{Lobachevsky State University of Nizhni Novgorod, Russia  \\
	\email{konstantin.barkalov@itmm.unn.ru},
	\email{ilya.lebedev@itmm.unn.ru},
	\email{maria.rachinskaya@itmm.unn.ru},
	\email{gergel@unn.ru}
}
